\begin{song}{500 Miles}{subtitle={When I Wake Up}, composer={The Proclaimers}, capo={2}}

Intro \\
\guitarChord{D} 1 2 3 4    \guitarChord{D} 2 2 3 4    \guitarChord{D} 3 2 3 4    \guitarChord{D} 4 2 3 4 \\

Verse 1 \\
When I \guitarChord{D}wake up, yeah, I \guitarChord{D}know I'm gonna be, \\
I'm gonna \guitarChord{G5}be the man who \guitarChord{A}wakes up next to \guitarChord{D}you. \\

When I \guitarChord{D}go out, yeah, I \guitarChord{D}know I'm gonna be, \\
I'm gonna \guitarChord{G}be the man who \guitarChord{A}goes along with \guitarChord{D}you. \\

If I \guitarChord{D}get drunk, well I \guitarChord{D}know I'm gonna be, \\
I'm gonna \guitarChord{G}be the man who \guitarChord{A}gets drunk next to \guitarChord{D}you. \\

And if I \guitarChord{D}haver, yeah, I \guitarChord{D}know I'm gonna be, \\
I'm gonna \guitarChord{G}be the man who's \guitarChord{A}havering to \guitarChord{D}you. \\

Chorus \\
But \guitarChord{D5}I would walk  five \guitarChord{D5}hund-red miles, and \\
\guitarChord{G5}I    would     walk    five \guitarChord{A}hund-red    more \\
Just to \guitarChord{D}be the man who walked a thousand \guitarChord{G}miles \\
to fall down \guitarChord{A}at your door.    \guitarChord{D5} \\

Verse 2 \\
When I'm \guitarChord{D}working, yeah, I \guitarChord{D}know I'm gonna be, \\
I'm gonna \guitarChord{G}be the man who's \guitarChord{A}working hard for \guitarChord{D}you. \\

And when the \guitarChord{D5}money,    comes in \guitarChord{D5}for the work I do \\
I'll pass al-\guitarChord{G5}most every \guitarChord{A}penny on to \guitarChord{D5}you. \\

When I \guitarChord{D5}come home, oh I \guitarChord{D5}know I'm gonna be, \\
I'm gonna \guitarChord{G5}be the man who \guitarChord{A}comes back home to \guitarChord{D5}you. \\

And if I \guitarChord{D5}grow old, well, I \guitarChord{D5}know I'm gonna be, \\
I'm gonna \guitarChord{G5}be the man who's \guitarChord{A}growing old with \guitarChord{D5}you. \\

Chorus \\
But \guitarChord{D5}I would walk five \guitarChord{D5}hundred-red miles, and \\
\guitarChord{G5}I would walk five \guitarChord{A}hundred-red more \\
Just to \guitarChord{D5}be the man who walked a thousand \guitarChord{G5}miles \\
to fall down \guitarChord{A}at your door.    \guitarChord{D5} \\

Bridge 1 \\
Da Da Da \guitarChord{D5}Da          Da Da Da \guitarChord{D5}Da      Da Da Da-\guitarChord{G5}Da-Da-La Da-Da-La \guitarChord{A}Da-Da-La La \guitarChord{D5}La \\

Da Da Da \guitarChord{D5}Da           Da Da Da \guitarChord{D5}Da      Da Da Da-\guitarChord{G5}Da-Da-La Da-Da-La \guitarChord{A}Da-Da-La La \guitarChord{D5}La \\

Verse 3 \\
When I'm \guitarChord{D5}lonely, well I know I'm gonna be \\
I'm gonna \guitarChord{G5}be the man who's \guitarChord{A}lonely without \guitarChord{D5}you \\
And when I'm \guitarChord{D5}dreaming, well I know I'm gonna dream \\
I'm gonna \guitarChord{G5}Dream about the \guitarChord{A}time when I'm with \guitarChord{D5}you \\

When I \guitarChord{D5}go out(When I go out), well I know I'm gonna be \\
I'm gonna \guitarChord{G5}be the man who \guitarChord{A}goes along with \guitarChord{D5}you \\
And when I \guitarChord{D5}come home(When I come home), yes I know I'm gonna be \\
I'm gonna \guitarChord{G5}be the man who \guitarChord{A}comes back home with \guitarChord{Bm}you \\
I'm gonna \guitarChord{Em7}be the man who's \guitarChord{A}coming home with \guitarChord{D5}you \\

Chorus \\
But \guitarChord{D5}I would walk five \guitarChord{D5}hund-red miles, and \\
\guitarChord{G5}I would walk five \guitarChord{A}hundred-red  more, \\
Just to \guitarChord{D5}be the man who walked a thousand  \guitarChord{G5}miles to \\
fall down \guitarChord{A}at your door   \guitarChord{D5} \\

Bridge 2 \\

Da Da Da \guitarChord{D5}Da          Da Da Da \guitarChord{D5}Da      Da Da Da-\guitarChord{G5}Da-Da-La Da-Da-La \guitarChord{A}Da-Da-La La \guitarChord{D5}La \\

Da Da Da \guitarChord{D5}Da           Da Da Da \guitarChord{D5}Da      Da Da Da-\guitarChord{G5}Da-Da-La Da-Da-La \guitarChord{A}Da-Da-La La \guitarChord{D5}La \\

Chorus \\
But \guitarChord{D5}I would walk five \guitarChord{D5}hund-red miles, and \\
\guitarChord{G5}I would walk five \guitarChord{A}hundred-red  more, \\
Just to \guitarChord{D5}be the man who walked a thousand  \guitarChord{G5}miles to \\
fall down \guitarChord{D} at \guitarChord{A} your \guitarChord{D} do  -  or \guitarChord{D} \\
\end{song}

\begin{song}{Sonne}{artist={Polkageist}}

\songComment{Intro} ~

\songComment{2x} ~

\guitarChord{Em}(Pf\guitarChord{Bm}eif\guitarChord{Em}en)\guitarChord{G}~\guitarChord{F#m} \\
\guitarChord{Em}(Bass-La\guitarChord{Bm}uf) \\
\end{song}

